---
title: 'RWORKSHEET #7a'
author: "Ann Erika D. Gabales"
date: "2022-12-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Create a data frame for the table below.
```{r }
df <- data.frame(Student = seq(1:10),
           PreTest = c(55,54,47,57,51,61,57,54,63,58),
           PostTest = c(61,60,56,63,56,63,59,56,62,61))
df
```

### a.Compute the descriptive statistics using different packages (Hmisc and pastecs).Write the codes and its result.
```{r }
library(Hmisc)
library(pastecs)

describe(df)

stat.desc(df)
```

## 2.The Department of Agriculture was studying the effects of several levels of a fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.
```{r }
DepartmentofAgriculture <- c(10,10,10,20,20,50,10,
                             20,10,50,20,50,20,10)
```

### a.Write the codes and describe the result.
```{r }
ordered_factor <- sort(DepartmentofAgriculture, decreasing = FALSE)
ordered_factor
```
**As what expected, the result was sorted in increasing number (from 10 to 50).**

## 3.Abdul Hassan, president of Floor Coverings Unlimited, has asked you to studythe exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” ,“l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense
###a. What is the best way to represent this in R?
```{r }
#DATAFRAME
Subjects <- c("l","n","n","i","l","l","n","n","i","l")

df <- data.frame(Subjects)
df
```

## 4. Sample of 30 tax accountants from all the states and territories of Australia andtheir individual state of origin is specified by a character vector of state mnemonics as:
```{r }
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")
```

### a. Apply the factor function and factor level. Describe the results.
```{r }
fcFunction <- factor(state)
fcFunction 
```
  **the vectors were factored and it also has been leveled.**
## 5. From #4 - continuation:
-Suppose we have the incomes of the same tax accountants in another vector (insuitably large units of money)
```{r }
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
```

### a. Calculate the sample mean income for each state we can now use the special function tapply():
````{r }
incmeans <- tapply(incomes, state, mean)
incmeans
```

### b. Copy the results and interpret.

**As what shown on the result, each has its own sample mean income.**

## 6. Calculate the standard errors of the state income means (refer again to number 3)
### a. What is the standard error? Write the codes.
```{r }
stdError <- function(x) sqrt(var(x)/length(x))
incster <- tapply(incomes, state, stdError)
incster
```

### b. Interpret the result.

**As what shown on the result, each state income means has standard errors.**

## 7. Use the titanic dataset.
```{r }
data("Titanic")
dfTitanic<- data.frame(Titanic)
```

### a. subset the titatic dataset of those who survived and not survived. Show the codes and its result.
```{r }
headSubset <- subset(dfTitanic, select = "Survived")
headSubset
```

## 8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically as Dr. Wolberg reports his clinical cases. The database therefore reflects this chronological grouping of the data. You can create this dataset in Microsoft Excel.
### a. describe what is the dataset all about.

**The dataset is all about the breast cancer Wisconsin whereasit can be seen the brief informations about the respondents who were diagnosed of Breast cancer.**

### b. Import the data from MS Excel. Copy the codes.
```{r }
library(readxl)
Breast_Cancer <- read_excel("C:/Users/asus/Desktop/GABALES_BSIT2A/Breast_Cancer.xlsx")
View(Breast_Cancer)
```

### c. Compute the descriptive statistics using different packages. Find the values of:
### c.1 Standard error of the mean for clump thickness.
```{r }
stdCLth <- stdError(Breast_Cancer$`CL. thickness`)
stdCLth
```

### c.2 Coefficient of variability for Marginal Adhesion.
```{r }
COV <- sd(Breast_Cancer$`Marg. Adhesion`) / mean(Breast_Cancer$`Marg. Adhesion`)* 100
COV
```

### c.3 Number of null values of Bare Nuclei.
```{r }
Null_Values <- subset(Breast_Cancer[ , 7], `Bare. Nuclei` == "NA")
Null_Values
```

### c.4 Mean and standard deviation for Bland Chromatin
```{r }
mean(Breast_Cancer$`Bl. Cromatin`)
sd(Breast_Cancer$`Bl. Cromatin`)
```

### c.5 Confidence interval of the mean for Uniformity of Cell Shape
```{r }
CalMean<- mean(Breast_Cancer$`Cell Shape`)
CalMean
```

### d. How many attributes?
```{r }
length(attributes(Breast_Cancer))
```

### e. Find the percentage of respondents who are malignant. Interpret the results.
```{r }
P_respond <- subset(Breast_Cancer, Class == "maligant")
P_respond

library(scales)
percent_respo <- 17  / 49
percent(percent_respo)
```

## 9. Export the data abalone to the Microsoft excel file. Copy the codes.
```{r }
library("AppliedPredictiveModeling")
data("abalone")
head(abalone)
summary(abalone)

dfabalone <- data.frame(abalone)

#Exporting the data abalone to the Microsoft excel file

library(xlsx)
write.xlsx(dfabalone, "C:/Users/asus/Desktop/GABALES_BSIT2A/Abalone.xlsx", col.names = TRUE)
```
